---
title: "Clustering Tennis Rackets"
author: "Masha"
date: "2/14/2020"
output: 
   md_document:
    variant: markdown_github
---
You are working as a statistical consultant for a tennis racquet manufacturer, helping with some
statistical analysis they hope can be of use in an upcoming advertising campaign. The company
has selected 31 new models of racquets produced by that company and others and measured six
variables, which represent various characteristics of the racquets:
• X1 – length of racquet (in inches)
• X2 – static weight (in ounces) – this is how much the racquet actually weighs on a scale
• X3 – balance (in inches) – this is a measure of whether the racquet is heavier in on the
head end or on the handle end; more negative values indicate a more head-heavy
racquet; positive values indicate a more head-light racquet; zero indicates an even
balance.
• X4 – swing weight – this is a complicated measure of how heavy the racquet feels when
it is swung.
• X5 – headsize (in square inches) – the size of the racquet face (the strung area)
• X6 – beamwidth (in mm) – the width of the cross-section (edge) of the racquet

QUESTION 1.
Are there particular racquet(s) that are highly unusual in terms of the measured
characteristics? If so, identify them.

```{r}
library(MASS)
library(lattice)
```

DATA
```{r}
Tennis.Racquets = read.csv("C:/Users/fb8502oa/Desktop/Github stuff/Cluster-Analysis/Tennis Racquets.csv")
head(Tennis.Racquets)
```

```{r}
summary(Tennis.Racquets)
```

looking for outlyers.
```{r}
outlyer = boxplot(Tennis.Racquets)$out 
outlyer
```
the outlayers are:
27.600 (length) = volklorganixv1oversize
-0.375 (balance) = dunlopBiomimetic700
125.00 (headsize) = Asics125



QUESTION 2.
Are there notable associations/relationships between some of the variables? (if so,
describe them and present them graphically)

```{r}
#finding correlation
library(corrplot)

Tennissub = Tennis.Racquets[, -c(1)]  # this is th subset that works well. 
Tennissub.cor = cor(Tennissub)
plot(corrplot(Tennissub.cor, order = "hclust"))
```

```{r}
cor(Tennissub)
```

Static weight and balance are moderately correlated while beam width, length, head size,
swing weight are strongly correlated.


QUESTION 3

Is there a way to graphically represent the raw data for the 31 racquets and draw
conclusions about the data set from such a graph?

```{r}
pca = princomp(Tennissub, cor = TRUE)
summary(pca)
```

```{r}
biplot(pca)
```

Length, beam width and head size are more correlated than swing weight, static weight and
balance
22 is an outlier.

QUESTION 4 & QUESTION 5
  Can we find a few indices that describe the variation in the data set using a lesser
dimension than the original set of variables?

? If so, what are those indices? Is there a convenient interpretation of any of the indices? 

```{r}
library(cluster)
library(factoextra)
library(FactoMineR)
Tennissub.mat = scale(Tennissub)
```

```{r}
tennis.PCA = PCA(Tennissub.mat, quali.sup = 1)
```

```{r}
summary(tennis.PCA)
```


the main area to focus on is 
```{r}
summary(pca)
```

Yes we can find indices that describe the variation in the dataset. The pca values the show total variation are 7. The 7 components explain total variation of the 31 racquets.

QUESTION 6
Can we graphically display the data in a low number of dimensions using such indices?
What conclusions about the racquets (individual racquets or groups of racquets) can you
draw from such a graph

```{r}
Tennissub.k15 =kmeans(Tennissub,15)
tennis.kmeans = kmeans(Tennissub.mat, 7)
fviz_cluster(tennis.kmeans,data=Tennissub)
```
```{r}
plot(fviz_pca_ind(tennis.PCA, col.ind = tennis.kmeans$cluster))
```

```{r}
View(Tennis.Racquets)
```

Question 7.
Can you find groups/clusters of similar racquets in terms of their characteristics? If so,
can you find a group of racquets that would be good novice players using the
specifications listed in part f ? 


```{r}
Tennissub.euc = dist(Tennissub.mat, method = "euclid")
cluster = agnes(Tennissub.euc, method = "ward")
```

```{r}
plot(cluster)
```

```{r}
par(ask =F)
```

```{r}
# h 
#k-maeans
wss = rep(0,8)
for(i in 1: 8)
  wss[i] = sum(kmeans(Tennissub.mat, centers = i)$withinss)
plot(1:8, wss, xlab = "number of cluster", ylab = "wss", type = "b")
```


as you can see, 5 is better than 8.
```{r}
Tennissub.k5 = kmeans(Tennissub.mat,5)
si = silhouette(Tennissub.k5$cluster, Tennissub.euc)
plot(si)
```































